---
title: "NSCLC_Outputs - S1"
author: "Hugo Pedder"
date: "2023-10-06"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  options(knitr.kable.NA = '\\-'),
  fig.height=5, 
  fig.width=7
  )
```
```{r, eval=FALSE, include=FALSE}
devtools::install_github("hugaped/BristolTAG")
```
```{r, include=FALSE}
library(BristolTAG)
library(survival)
library(ggplot2)
library(tidyverse)
```

## Load model results

```{r}
modseq1 <- readRDS(file="JAGS_Results/S1_PFS_fpoly1.RDS")
modseq2 <- readRDS(file="JAGS_Results/S1_PFS_fpoly2.RDS")
modseq <- append(modseq1, modseq2)
class(modseq) <- "sequence.fpoly"
```


## Load dataset

```{r}
ipd <- attributes(modseq[[1]])$ipd

anova <- anova_data(timepoints=seq(0,72, by=1),
                    df=ipd)
```

## Log-log plots

```{r, fig.cap="Log-log plots for PFS for studies included in node S1. Separation of the two lines indicates violation of the proportional hazards assumption"}
ipd <- attr(modseq1[[1]], "ipd")

loglog_plot(ipd)
```


## Model fit statistics

```{r}
modfit <- summary(modseq)

noconv <- subset(modfit, converged==FALSE)
modfit <- subset(modfit, converged==TRUE)

modfit <- rbind(summary(modseq1), summary(modseq2))

# Drop models with errors
modfit <- modfit[!is.na(modfit$converged),]

modfit <- arrange(modfit, DIC)

candmod <- modfit[c(2,3),]
```

```{r}
# Only report FP powers
knitr::kable(modfit[,c(-1,-7)], col.names=c("Power 1", "Power 2", "Residual deviance", "pV", "DIC"),
                  digits=1, 
                  caption=paste0("Model fit statistics for successfully converged fractional polynomial models run on PFS for node S1. Power 1 and Power 2 represent fractional polynomial powers. 1st order fractional polynomials only have a single power parameter (Power 1). Total number of data points = ", nrow(anova$aggregate)))
```

The model that clearly has the best statistical fit is FP_0.5_-0.5, though we will include the 4 models with the lowest DIC as candidates:

```{r}
knitr::kable(candmod[,c(-1,-7)], col.names=c("Power 1", "Power 2", "Residual deviance", "pV", "DIC"),
                  digits=1, 
                  caption=paste0("Model fit statistics for candidate fractional polynomial models run on PFS for node S1. Power 1 and Power 2 represent fractional polynomial powers. 1st order fractional polynomials only have a single power parameter (Power 1). Total number of data points = ", nrow(anova$aggregate)))
```


## Plots of time-varying HRs

These are shown only for the candidate models, but additional ones could be specified here.

```{r}
hazardrats <- data.frame()
for (mod in seq_along(candmod$model)) {
  hr <- hrcalc(modseq[[candmod$model[mod]]], times=seq(1, 60, length.out = 100), eform=TRUE)
  hr <- hr$summary %>% mutate(model=candmod$model[mod])
  hazardrats <- rbind(hazardrats, hr)
}
```


Plot panels of time-varying HRs for candidate models:

```{r}
reftrt <- "PCT"

out.df <- hazardrats

trtnames <- attr(modseq[[1]], "trtnames")

out.df$trt1 <- factor(out.df$trt1, labels=trtnames, levels=trtnames)

cols <- RColorBrewer::brewer.pal(dplyr::n_distinct(out.df$trt1), "Set1")

out.df <- subset(out.df, trt2==reftrt)
cols <- cols[unique(as.numeric(out.df$trt1))]

out.df$model <- factor(out.df$model)

g <- ggplot2::ggplot(out.df, ggplot2::aes(x=time, 
                                          #ymin=`97.5%`, ymax=`2.5%`, # Commenting out makes y-axis scales better
                                          y=`50%`,
                        color=trt1, fill=trt1, linetype=trt1)) +
  ggplot2::geom_line() +
  #ggplot2::geom_ribbon(alpha=0.3) +
  ggplot2::facet_wrap(~model) +
  ggplot2::xlab("Time") +
  ggplot2::ylab("HR") +
  ggplot2::theme_bw() +
  ggplot2::ggtitle(paste0("Time-varying relative effects vs treatment ", unique(out.df$trt2))) +
  ggplot2::scale_fill_manual(name = "Treatment", values=cols) +
  ggplot2::scale_color_manual(name = "Treatment", values=cols) +
  ggplot2::scale_linetype_discrete(name = "Treatment")

plot(g)
```

Looking at the implied HRs, the model with the lowest DIC (FP_0.5_-0.5) has potentially the least plausible HRs in the long-term, since they continue to increase.

A more reasonable model may be FP_-0.5_0 or FP_0_-0.5, both of which have very similar shapes of implied HRs.

Time-varying HRs for a single plausible model with lowest DIC (if needed):

```{r, fig.cap="Time-varying (implied) hazard ratios for all treatments versus PCT, estimated from 2nd order fractional polynomial (-0.5, 0) of PFS for S1. Shaded regions represent 95%CrIs"}
hazardrats <- hrcalc(modseq[[candmod$model[2]]], times=seq(1, 60, length.out = 100), eform=TRUE)
g <- plot(hazardrats, reftrt="PCT")
g + geom_line(linewidth=0.8)
```


## Plots of survival predictions for different models

```{r}
surv <- data.frame()
for (mod in seq_along(candmod$model)) {
  smod <- survcalc(modseq[[candmod$model[mod]]], refstudy="KEYNOTE407", 
                times=seq(1, 60, length.out = 100))
  smod2 <- smod$S %>% mutate(model=candmod$model[mod])
  surv <- rbind(surv, smod2)
}
```

```{r}
out.df <- surv

trtnames <- attr(modseq[[1]], "trtnames")
out.df$treatment <- factor(out.df$treatment, labels=trtnames, levels=trtnames)

# Define colours
cols <- RColorBrewer::brewer.pal(dplyr::n_distinct(trtnames), "Set1")

# Subset by treatments
# out.df <- subset(out.df, treatment %in% treats)
cols <- cols[unique(as.numeric(out.df$treatment))]

out.df$model <- factor(out.df$model)

# capt <- paste0("Fractional polynomial; P1 = ", surv$P1, ifelse(!is.null(surv$P2), paste0(", P2 = ", surv$P2), ""))
# capt <- paste(capt, paste("Reference study:", attr(surv, "refstudy")), sep="\n")
capt <-paste("Reference study:", attr(smod, "refstudy"))

g <- ggplot2::ggplot(out.df, ggplot2::aes(x=time, ymin=`97.5%`, ymax=`2.5%`, y=`50%`,
                        color=treatment, fill=treatment, linetype=treatment)) +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(~model) +
  ggplot2::xlab("Time") + ggplot2::ylab("PFS") +
  ggplot2::theme_bw() +
  ggplot2::scale_fill_manual(name = "Treatment", values=cols) +
  ggplot2::scale_color_manual(name = "Treatment", values=cols) +
  ggplot2::scale_linetype_discrete(name = "Treatment") +
  ggplot2::labs(caption=capt)

plot(g)
```


## Plot of survival predictions and KM data for each study, and for reference study

Plot with KM for plausible model with lowest DIC:

```{r, results="hide", fig.cap="Predicted survival curves for IMpower150, estimated from 2nd order fractional polynomial of PFS for S1. Survival predictions are plotted as coloured lines with shaded 95%CrIs. Kaplan-Meier data from the study are plotted as black solid lines."}
surv <- survcalc(modseq[[candmod$model[2]]], times=seq(1, max(ipd$time[ipd$study=="KEYNOTE407"]), length.out = 100),
                 refstudy="KEYNOTE407")
g <- plot(surv, quantity = "S", treats = c("PPCT", "PCT"), overlay.km = TRUE) +
  ylab("PFS")
plot(g)
```

Model fit is quite poor to the KM data at earlier follow-up, due to the extremely variable hazards at these times. The FP model cannot account for this. It is possible here that a spline model (e.g. M-splines) may provide a better fit here.


## Model fit results for UME

No closed loops for this network

## Dev-dev plots for UME vs NMA

No closed loops for this network


## Predicted survival curves for selected model with extrapolation

I'll just choose one here.

```{r, results="hide", fig.cap="Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial of PFS for all treatments at S1."}
surv <- survcalc(modseq[[candmod$model[1]]], times=seq(1, 52*3, length.out = 100),
                 refstudy="KEYNOTE407")
g <- plot(surv, quantity = "S", plotinterval = FALSE,
          treats=c("PPCT", "PCT", "ABCP")) + geom_line(linewidth=1) +
  ylab("PFS")
plot(g)
```


Median survival for each treatment within selected model:

```{r}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq[[candmod$model[1]]], refstudy="KEYNOTE407",
                 quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```





## Parameter estimates from selected model

```{r}
finalmod <- modseq[[candmod$model[1]]]

# Mu
params <- rownames(finalmod$BUGSoutput$summary)[grepl("^mu\\[", rownames(finalmod$BUGSoutput$summary))]

# D
params <- c(params, rownames(finalmod$BUGSoutput$summary)[grepl("^d\\[", rownames(finalmod$BUGSoutput$summary))])

# Create parameter names
paramnams <- params
for (i in seq_along(attr(finalmod, "studynames"))) {
  paramnams <- gsub(paste0("^mu\\[", i, "\\,"), paste0("mu[", attr(finalmod, "studynames")[i], ","),
                  paramnams)
}
for (k in seq_along(attr(finalmod, "trtnames"))) {
  paramnams <- gsub(paste0("^d\\[", k, "\\,"), paste0("d[", attr(finalmod, "trtnames")[k], ","),
                  paramnams)
}

param.df <- finalmod$BUGSoutput$summary[params, c("mean", "sd", "2.5%", "50%", "97.5%")]
rownames(param.df) <- paramnams

# Kable it up
knitr::kable(param.df, col.names=c("Mean", "SD", "2.5%", "Median", "97.5%"),
                  digits=2, 
                  caption="Parameter estimates for selected 2nd order fractional polynomial (-0.5, -0.5). mu represent the study-specific baselines and d the treatment effect versus PPCT, for each fractional polynomial coefficient. Posterior quantiles (median, 2.5% and 95.5%) are shown.")
```


## Outputting results for use in economic model

### Tests for multivariate normality (on a sample of MCMC iterations)

```{r, echo=TRUE}
library(MVN)

set.seed(890421)
samp <- sample(1:nrow(finalmod$BUGSoutput$sims.matrix), 2000)
nt <- 2
ns <- 1

cols <- c(paste0("d[", 2:nt, ",", 1, "]"), 
          paste0("d[", 2:nt, ",", 2, "]"), 
          paste0("d[", 2:nt, ",", 3, "]"),
          paste0("mu[", 1:ns, ",", 1, "]"),
          paste0("mu[", 1:ns, ",", 2, "]"),
          paste0("mu[", 1:ns, ",", 3, "]"))
temp <- finalmod$BUGSoutput$sims.matrix[samp, cols]

result <- mvn(temp, mvnTest="hz", 
              multivariatePlot = "qq")

result$multivariateNormality

result$univariateNormality

```

It looks as though we can assume multivariate normal in this case, so we can provide the CfG team with parameters for a multivariate normal distribution that they can sample from.


### Multivariate normal parameters from selected model

These will be saved to an excel file.

```{r}
library(officer)

info.df <- data.frame("Title"=c("Fractional polynomial multivariate normal distribution of MCMC samples - means and covariances for key model parameters",
                                      # "Parameters named by the study name refer to the reference study ('baseline') effect for each fractional polynomial coefficient (1-3)",
                                      paste0("Parameters named by the treatment refer to the relative treatment effect for each fractional polynomial coefficient (1-3) versus the network reference (", attributes(modseq[[1]])$trtnames[1], ")")))

# Choose save location
wb <- openxlsx::createWorkbook(title="S1")
openxlsx::addWorksheet(wb=wb, sheetName="Info")
openxlsx::writeDataTable(wb=wb, sheet="Info", 
                         x=info.df)

for (i in 1:nrow(candmod)) {
  
  mod <- modseq[[candmod$model[i]]]
  
  sheetnam <- paste("FP", mod$model$data()$P1, mod$model$data()$P2, sep="_")
  openxlsx::addWorksheet(wb=wb, sheetName=sheetnam)
  
  # mvn <- output_coda_fp(mod, format="mvn",
  #                       refstudy="KEYNOTE407",
  #                       treatments=c("PPCT", "PCT"))
  
  mvn <- output_coda_fp(mod, format="mvn",
                        refstudy=NULL,
                        treatments=c("PPCT", "PCT"))
  
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$mean), rowNames = TRUE)
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$covar), startCol=4,
                           rowNames = TRUE, colNames = TRUE)
}

openxlsx::saveWorkbook(wb=wb, file="MVN_S1.xlsx", overwrite=TRUE)
```
