---
title: "NSCLC_Outputs - ST2 PFS, assuming no histology effect modification"
author: f("Hugo Pedder", "Ayman Sadek", "Nicky J Welton")
date: "2024-01-31"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  options(knitr.kable.NA = '\\-'),
  fig.height=5, 
  fig.width=7
  )
```
```{r, eval=FALSE, include=FALSE}
devtools::install_github("hugaped/BristolTAG")
```
```{r, include=FALSE}
library(BristolTAG)
library(survival)
library(ggplot2)
library(tidyverse)
source("NSCLC_functions.R")

all.cols <- RColorBrewer::brewer.pal(9, "Set1")
all.cols <- c(all.cols, RColorBrewer::brewer.pal(4, "Set2"))
```

The models in Analysis 1 fit fractional polynomial models that relax the proportional hazards assumption. They assume no effect of histology (i.e. they do not differentiate between studies of Non-squamous or Squamous patients).

## Load model results

```{r}
modseq1 <- readRDS(file="JAGS_Results/ST2_PFS_fpoly1_Analysis1.RDS")
modseq2 <- readRDS(file="JAGS_Results/ST2_PFS_fpoly2_Analysis1.RDS")
modseq <- append(modseq1, modseq2)
class(modseq) <- "sequence.fpoly"
```


## Load dataset

```{r}
ipd <- attributes(modseq[[1]])$ipd

anova <- anova_data(timepoints=seq(0,16, by=1),
                    df=ipd)
```

## Log-log plots

```{r, fig.cap="Log-log plots for PFS for studies included in node ST2. Separation of the two lines indicates violation of the proportional hazards assumption"}
ipd <- attr(modseq1[[1]], "ipd")

loglog_plot(ipd)
```


## Model fit statistics

```{r}
modfit <- summary(modseq)

noconv <- subset(modfit, converged==FALSE)
modfit <- subset(modfit, converged==TRUE)

modfit <- rbind(summary(modseq1), summary(modseq2))

# Drop models with errors
modfit <- modfit[!is.na(modfit$converged),]

modfit <- arrange(modfit, DIC)

candmod <- modfit[c(1,2,4),]
```

```{r}
# Only report FP powers
knitr::kable(modfit[,c(-1,-7)], col.names=c("Power 1", "Power 2", "Residual deviance", "pV", "DIC"),
                  digits=1, 
                  caption=paste0("Model fit statistics for successfully converged fractional polynomial models run on PFS for node ST2. Power 1 and Power 2 represent fractional polynomial powers. 1st order fractional polynomials only have a single power parameter (Power 1). Total number of data points = ", nrow(anova$aggregate)))
```

Based on this, candidate models are the following:

```{r}
knitr::kable(candmod[,c(-1,-7)], col.names=c("Power 1", "Power 2", "Residual deviance", "pV", "DIC"),
                  digits=1, 
                  caption=paste0("Model fit statistics for candidate fractional polynomial models run on PFS for nodes node ST2. Power 1 and Power 2 represent fractional polynomial powers. 1st order fractional polynomials only have a single power parameter (Power 1). Total number of data points = ", nrow(anova$aggregate)))
```


## Plots of time-varying HRs

```{r}
all.treats <- attr(modseq[[1]], "trtnames")
```

These are shown only for the 4 candidate models, but additional ones could be specified here. Note that the model estimates treatment effects for all treatments regardless of the specific prognostic population (e.g. squamous, non-squamous).

```{r}
times <- seq(1, 52, length.out = 100)

hazardrats <- data.frame()
for (mod in seq_along(candmod$model)) {
  hr <- hrcalc(modseq[[candmod$model[mod]]], times=times, eform=TRUE)
  hr <- hr$summary %>% mutate(model=candmod$model[mod])
  hazardrats <- rbind(hazardrats, hr)
}
```

Plot panels of time-varying HRs for candidate models:

```{r}
g <- plot_hazardmodels(hazardrats, all.treats=all.treats,
                       reftrt="Docetaxel")

plot(g)
```


Time-varying HRs for a single plausible model with lowest DIC (if needed):

```{r}
hazardrats <- hrcalc(modseq[[candmod$model[1]]], times=seq(1, 52, length.out = 100), eform=TRUE)
```
```{r, fig.cap="Time-varying (implied) hazard ratios for all treatments versus Chemotherapy, estimated from 2nd order fractional polynomial of PFS for ST1 excl CHECKMATE-078. Shaded regions represent 95%CrIs"}
g <- plot(hazardrats, reftrt="Docetaxel")
g + geom_line(linewidth=0.8)
```

# Survival predictions

## Plot of survival predictions and KM data for each study

Plot with KM for plausible model with lowest DIC, 2nd order fractional polynomial:

Fit seems really quite poor here to the study...PFS prediction doesn't seem to match the KM data that well.

```{r, results="hide", fig.cap="Predicted survival curves for included studies estimated from selected 2nd order fractional polynomial of PFS for ST2. Survival predictions are plotted as coloured lines with shaded 95%CrIs. Kaplan-Meier data from the study are plotted as black solid lines. Note that this plot does not include predictions from treatments modelled using proportional hazards"}
g <- studykm_survplot(modseq[[candmod$model[1]]]) +
  geom_km(anova$ipd) +
  ylab("PFS")
plot(g)
```


## Survival predictions for non-squamous patients (ST2)

Selected reference study for ST2 non-squamous patients is the non-squamous subgroup of **LUME-Lung 1**

```{r}
all.treats <- attributes(modseq[[1]])$trtnames
plot.treats <- all.treats
```

```{r}
refseq <- readRDS("JAGS_Results/ST2_PFS_fpoly2_LUMELung1.NS.RDS")
refstudy <- "LUME-Lung1"
```

### Plots of survival predictions for different models (ST2, Non-squamous)

```{r}
surv <- data.frame()
for (mod in seq_along(candmod$model)) {
  smod <- survcalc(modseq[[candmod$model[mod]]], refstudy=refstudy, 
                   refmod = refseq[[candmod$model[mod]]],
                times=seq(1, 52, length.out = 100))
  smod2 <- smod$S %>% mutate(model=candmod$model[mod])
  surv <- rbind(surv, smod2)
}
```

```{r}
g <- plot_survivalmods(surv.df=surv, 
                       all.treats=all.treats, plot.treats=plot.treats,
                       refstudy=attr(smod, "refstudy")
                       )

plot(g)
```


### Predicted survival curves for selected model with extrapolation (ST2, Non-squamous)

I'll just choose one here.

```{r, results="hide", fig.cap="Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST2."}
surv <- survcalc(modseq[[candmod$model[1]]], times=seq(1, 52, length.out = 100),
                 refmod=refseq[[candmod$model[1]]],
                 refstudy=refstudy
                 )


g <- plot(surv, quantity = "S", plotinterval = FALSE, treats=plot.treats) + 
  geom_line(linewidth=1) +
  ylab("PFS")
plot(g)
```

Median survival for each treatment within selected model:

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq[[candmod$model[1]]], refstudy=refstudy,
                 quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


## Survival predictions for squamous patients (ST2)

Selected reference study for ST2 squamous patients is the squamous subgroup of **LUME-Lung1**

```{r}
all.treats <- attributes(modseq[[1]])$trtnames
plot.treats <- all.treats
```

```{r}
refseq <- readRDS("JAGS_Results/ST2_PFS_fpoly2_LUMELung1.S.RDS")
refstudy <- "LUME-Lung1"
```

### Plots of survival predictions for different models (ST2, Squamous)

```{r}
surv <- data.frame()
for (mod in seq_along(candmod$model)) {
  smod <- survcalc(modseq[[candmod$model[mod]]], refstudy=refstudy,
                   refmod=refseq[[candmod$model[mod]]],
                times=seq(1, 52, length.out = 100))
  smod2 <- smod$S %>% mutate(model=candmod$model[mod])
  surv <- rbind(surv, smod2)
}
```

```{r}
g <- plot_survivalmods(surv.df=surv, 
                       all.treats=all.treats, plot.treats=plot.treats,
                       refstudy=attr(smod, "refstudy")
                       )

plot(g)
```


### Predicted survival curves for selected model with extrapolation (ST2, Squamous)

I'll just choose one here.

```{r, results="hide", fig.cap="Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST2."}
surv <- survcalc(modseq[[candmod$model[1]]], times=seq(1, 52, length.out = 100),
                 refmod=refseq[[candmod$model[1]]],
                 refstudy=refstudy
                 )
g <- plot(surv, quantity = "S", plotinterval = FALSE, treats="Docetaxel") + 
  geom_line(linewidth=1) +
  ylab("PFS")
plot(g)
```

Median survival for each treatment within selected model:

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq[[candmod$model[1]]], refstudy=refstudy,
                 quantile=0.5, interval=c(0.1,100), treatments = plot.treats)
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Multivariate normal parameters from candidate (ST2)

These will be saved to an excel file.

```{r}
library(officer)

info.df <- data.frame("Title"=c("Fractional polynomial multivariate normal distribution of MCMC samples - means and covariances for key model parameters",
                                      "Parameters named by the study name refer to the reference study ('baseline') effect for each fractional polynomial coefficient (1-3)",
                                      "Parameters named by the treatment refer to the relative treatment effect for each fractional polynomial coefficient (1-3)"))

# Choose save location
wb <- openxlsx::createWorkbook(title="ST2_PFS_Analysis1")
openxlsx::addWorksheet(wb=wb, sheetName="Info")
openxlsx::writeDataTable(wb=wb, sheet="Info", 
                         x=info.df)

for (i in 1:nrow(candmod)) {
  
  mod <- modseq[[candmod$model[i]]]
  
  sheetnam <- paste("FP", mod$model$data()$P1, mod$model$data()$P2, sep="_")
  openxlsx::addWorksheet(wb=wb, sheetName=sheetnam)
  
  mvn <- output_coda_fp(mod, format="mvn",
                        refstudy=NULL,
                        treatments=plot.treats)
  
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$mean), rowNames = TRUE)
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$covar), startCol=4,
                           rowNames = TRUE, colNames = TRUE)
}

openxlsx::saveWorkbook(wb=wb, file="MVN_ST2_PFS_Analysis1.xlsx", overwrite=TRUE)
```


## Model fit results for UME (ST2)

No closed loops for this network

### Dev-dev plots for UME vs NMA (ST2)

No closed loops for this network
