---
title: "NSCLC Survival Predictions - ST1 (PDL1 >50%, PDL1 1-49% & PDL1 <1%)"
author: f("Hugo Pedder", "Ayman Sadek", "Nicky J Welton")
date: "2024-01-05"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  options(knitr.kable.NA = '\\-'),
  fig.height=5, 
  fig.width=7
  )
```
```{r, eval=FALSE, include=FALSE}
devtools::install_github("hugaped/BristolTAG")
```
```{r, include=FALSE}
library(BristolTAG)
library(survival)
library(ggplot2)
library(tidyverse)
source("NSCLC_functions.R")

all.cols <- RColorBrewer::brewer.pal(9, "Set1")
all.cols <- c(all.cols, RColorBrewer::brewer.pal(4, "Set2"))
```


## Load model results

```{r}
# modseq1 <- readRDS(file="JAGS_Results/ST1_AllPDL_PFS_fpoly1.RDS")
# modseq2 <- readRDS(file="JAGS_Results/ST1_AllPDL_PFS_fpoly2.RDS")
# modseq <- append(modseq1, modseq2)
# class(modseq) <- "sequence.fpoly"

# Only need to load 2nd order models for this
modseq <- readRDS(file="JAGS_Results/ST1_AllPDL_PFS_fpoly2.RDS")

# Remove ZZ from study name
for (mod in seq_along(modseq)) {
  attributes(modseq[[mod]])$study <- 
    gsub("(ZZ)(.+)(_>1%)", "\\2", attributes(modseq[[mod]])$study)
  
  attributes(modseq[[mod]])$studynames <- 
    gsub("(ZZ)(.+)(_>1%)", "\\2", attributes(modseq[[mod]])$studynames)

  attributes(modseq[[mod]])$ipd$study <- 
    gsub("(ZZ)(.+)(_>1%)", "\\2", attributes(modseq[[mod]])$ipd$study)
  
  # Set mu[,2,] to be equal to mu[,1,] for mixed PDL studies (>1%)
  # This ensures survival predictions will work properly, but note that if using survcalc() with a named refstudy it will therefore always use PDL1 >50% baseline
  modseq[[mod]]$BUGSoutput$sims.list$mu[,,2,] <- modseq[[mod]]$BUGSoutput$sims.list$mu[,,1,]
}
```

```{r}
# Select the correct treatment parameters
modseq.50 <- modseq
modseq.1 <- modseq
modseq.0 <- modseq
for (mod in seq_along(modseq)) {
  if (class(modseq[[mod]]) %in% "rjags") {
    modseq.50[[mod]] <- select_pdl1(modseq.50[[mod]], pdl1=">50%")
    modseq.1[[mod]] <- select_pdl1(modseq.1[[mod]], pdl1="1-49%")
    modseq.0[[mod]] <- select_pdl1(modseq.0[[mod]], pdl1="<1%")
  }
}
```

```{r}
# 2nd order FP reference models
refseq.ns <- readRDS(file="JAGS_Results/ST1_PFS_fpoly2_CM057.RDS")
refseq.s <- readRDS(file="JAGS_Results/ST1_PFS_fpoly2_CM017.RDS")
refseq.ret <- readRDS(file="JAGS_Results/ST1_PFS_fpoly2_LIBRETTO-001.RDS")
```

## Load dataset

```{r}
ipd <- attributes(modseq[[1]])$ipd

anova <- anova_data_st1(timepoints=seq(0,72, by=1),
                    df=ipd)
```

```{r}
hrmod <- readRDS(file="JAGS_Results/ST1_PFS_HR_Non-squamous_Genetic.RDS")

d <- hrmod$BUGSoutput$sims.list$d
```

```{r}
ipd <- attr(modseq[[1]], "ipd")
ipd$study <- gsub("ZZ", "", ipd$study)
```

```{r}
all.treats <- attributes(modseq[[1]])$trtnames
ns.treats <- c("Docetaxel", "Pemetrexed", "Pemetrexed + Carboplatin", "Selpercatinib")
all.treats <- c(all.treats, ns.treats[2:length(ns.treats)])
```

## Model fit statistics

```{r}
modfit <- sumst1.sequence.fpoly(modseq, pdl.dev=TRUE)

noconv <- subset(modfit, is.na(converged))
modfit <- subset(modfit, converged==TRUE)

#modfit <- summary(modseq)
#modfit <- rbind(summary(modseq1), summary(modseq2))

# Drop models with errors
#modfit <- modfit[!is.na(modfit$converged),]

modfit <- arrange(modfit, DIC)

candmod <- modfit[c(1, 3, 5, 7),]
```


# Survival predictions for ST1, Non-squamous, PDL1 >50%, No genetic subtype

Selected reference for ST1 non-squamous population is the overall (not PDL1-subgrouped) Docetaxel arm of **CHECKMATE-057**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib",
#                                              "Sotorasib")]
plot.treats <- c("Atezolizumab", "Pembrolizumab", "Nivolumab", "Docetaxel", 
                 "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.50
finalmod <- candmod$model[1]
refmod <- refseq.ns[[finalmod]]
refstudy <- "CHECKMATE057"
pdl1 <- ">50%"
mutation <- "no genetic"
hist <- "non-squamous"
times <- seq(1, 52*3, length.out = 100)
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Survival predictions for ST1, Non-squamous, PDL1 1-49%, No genetic subtype

Selected reference for ST1 non-squamous population is the overall (not PDL1-subgrouped) Docetaxel arm of **CHECKMATE-057**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib",
#                                              "Sotorasib")]
plot.treats <- c("Atezolizumab", "Pembrolizumab", "Nivolumab", "Docetaxel", 
                 "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.1
finalmod <- candmod$model[1]
refmod <- refseq.ns[[finalmod]]
refstudy <- "CHECKMATE057"
pdl1 <- "1-49%"
mutation <- "no genetic"
hist <- "non-squamous"
times <- seq(1, 52*3, length.out = 100)
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Survival predictions for ST1, Non-squamous, PDL1 <1%, No genetic subtype

Selected reference for ST1 non-squamous population is the overall (not PDL1-subgrouped) Docetaxel arm of **CHECKMATE-057**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib",
#                                              "Sotorasib",
#                                              "Pembrolizumab",
#                                              "Nivolumab")]
plot.treats <- c("Atezolizumab", "Docetaxel", 
                 "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.0
finalmod <- candmod$model[1]
refmod <- refseq.ns[[finalmod]]
refstudy <- "CHECKMATE057"
pdl1 <- "<1%"
mutation <- "no genetic"
hist <- "non-squamous"
times <- seq(1, 52*3, length.out = 100)
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```



# Survival predictions for ST1, Squamous, PDL1 >50%, No genetic subtype

Selected reference for ST1 squamous population is the overall (not PDL1-subgrouped) Docetaxel arm of **CHECKMATE-017**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib",
#                                              "Sotorasib")]
plot.treats <- c("Nivolumab", "Atezolizumab", "Pembrolizumab", "Docetaxel", "Pacltxl-Carb")

modseq.i <- modseq.50
finalmod <- candmod$model[1]
refmod <- refseq.s[[finalmod]]
refstudy <- "CHECKMATE017"
pdl1 <- ">50%"
mutation <- "no genetic"
hist <- "squamous"
times <- seq(1, 52*3, length.out = 100)
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Survival predictions for ST1, Squamous, PDL1 1-49%, No genetic subtype

Selected reference for ST1 squamous population is the overall (not PDL1-subgrouped) Docetaxel arm of **CHECKMATE-017**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib",
#                                              "Sotorasib")]
plot.treats <- c("Nivolumab", "Atezolizumab", "Pembrolizumab", "Docetaxel", "Pacltxl-Carb")

modseq.i <- modseq.1
finalmod <- candmod$model[1]
refmod <- refseq.s[[finalmod]]
refstudy <- "CHECKMATE017"
pdl1 <- "1-49%"
mutation <- "no genetic"
hist <- "squamous"
times <- seq(1, 52*3, length.out = 100)
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Survival predictions for ST1, Squamous, PDL1 <1%, No genetic subtype

Selected reference for ST1 squamous population is the overall (not PDL1-subgrouped) Docetaxel arm of **CHECKMATE-017**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib",
#                                              "Sotorasib",
#                                              "Pembrolizumab")]
plot.treats <- c("Nivolumab", "Atezolizumab", "Docetaxel", "Pacltxl-Carb")

modseq.i <- modseq.0
finalmod <- candmod$model[1]
refmod <- refseq.s[[finalmod]]
refstudy <- "CHECKMATE017"
pdl1 <- "<1%"
mutation <- "no genetic"
times <- seq(1, 52*3, length.out = 100)
hist <- "squamous"
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```



# Survival predictions for ST1, Non-squamous, PDL1 >50%, KRAS

Selected reference for ST1 KRAS (non-squamous) population is the Docetaxel arm of **CODEBREAK 200**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib")]
plot.treats <- c("Sotorasib", "Atezolizumab", "Pembrolizumab", "Nivolumab", 
                 "Docetaxel", "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.50
finalmod <- candmod$model[1]
refmod <- modseq.i[[finalmod]]
refstudy <- "CODEBREAK200"
pdl1 <- ">50%"
mutation <- "KRAS"
times <- seq(1, 52*3, length.out = 100)
hist <- "non-squamous"
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Survival predictions for ST1, Non-squamous, PDL1 1-49%, KRAS

Selected reference for ST1 KRAS (non-squamous) population is the Docetaxel arm of **CODEBREAK 200**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib")]
plot.treats <- c("Sotorasib", "Atezolizumab", "Pembrolizumab", "Nivolumab", 
                 "Docetaxel", "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.1
finalmod <- candmod$model[1]
refmod <- modseq.i[[finalmod]]
refstudy <- "CODEBREAK200"
pdl1 <- "1-49%"
mutation <- "KRAS"
times <- seq(1, 52*3, length.out = 100)
hist <- "non-squamous"
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Survival predictions for ST1, Non-squamous, PDL1 <1%, KRAS

Selected reference for ST1 KRAS (non-squamous) population is the Docetaxel arm of **CODEBREAK 200**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Selpercatinib",
#                                              "Pembrolizumab",
#                                              "Nivolumab")]
plot.treats <- c("Sotorasib", "Atezolizumab", "Docetaxel", 
                 "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.0
finalmod <- candmod$model[1]
refmod <- modseq.i[[finalmod]]
refstudy <- "CODEBREAK200"
pdl1 <- "<1%"
mutation <- "KRAS"
times <- seq(1, 52*3, length.out = 100)
hist <- "non-squamous"
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
g <- plot_st1_survival(modseq.i=modseq.i[[finalmod]], 
                  times=times, 
                  refstudy=refstudy, 
                  refmod=refmod,
                  d=d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


# Survival predictions for ST1, Non-squamous, PDL1 >50%, RET fusion +

Selected reference for ST1 RET fusion + (non-squamous) population is Selpercatinib from **LIBRETTO-001**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Sotorasib")]
plot.treats <- c("Selpercatinib", "Atezolizumab", "Pembrolizumab", "Nivolumab",
                 "Docetaxel", "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.50
finalmod <- candmod$model[1]
refmod <- refseq.ret[[finalmod]]
refstudy <- "LIBRETTO-001"
pdl1 <- ">50%"
mutation <- "RET fusion +ve"
times <- seq(1, 52*3, length.out = 100)
hist <- "non-squamous"
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
hrnames <- attributes(hrmod)$trtnames

# Select d values for Docteaxel vs Selpercatinib
adj.d <- d[,which(hrnames=="Selpercatinib"), drop=FALSE]

# Adjust FP model to make it relative to Selpercatinib by applying constant HR
adj.jagsmod <- fp_applyhr(d=adj.d, # Docetaxel vs Selpercatinib
                          jagsmod=modseq.i[[finalmod]],
                          refmod=refmod,
                          reftrt="Selpercatinib"
                          )

adj.d <- apply(d[,-which(hrnames=="Selpercatinib"), drop=FALSE],
               MARGIN=2, 
               FUN=function(x) {x-adj.d})
adj.d <- cbind(matrix(0, ncol=1, nrow=nrow(adj.d)), adj.d)


g <- plot_st1_survival(modseq.i=adj.jagsmod, 
                  times=seq(1, 52*3, length.out = 100), 
                  refstudy=refstudy, 
                  refmod=refmod,
                  trtnames = hrnames[c(4,1:3)], # Treatment names of constant HR
                  d=adj.d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```


```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```



# Survival predictions for ST1, Non-squamous, PDL1 1-49%, RET fusion +

Selected reference for ST1 RET fusion + (non-squamous) population is Selpercatinib from **LIBRETTO-001**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Sotorasib")]
plot.treats <- c("Selpercatinib", "Atezolizumab", "Pembrolizumab", "Nivolumab",
                 "Docetaxel", "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.1
finalmod <- candmod$model[1]
refmod <- refseq.ret[[finalmod]]
refstudy <- "LIBRETTO-001"
pdl1 <- "1-49%%"
mutation <- "RET fusion +ve"
times <- seq(1, 52*3, length.out = 100)
hist <- "non-squamous"
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
hrnames <- attributes(hrmod)$trtnames

# Select d values for Docteaxel vs Selpercatinib
adj.d <- d[,which(hrnames=="Selpercatinib"), drop=FALSE]

# Adjust FP model to make it relative to Selpercatinib by applying constant HR
adj.jagsmod <- fp_applyhr(d=adj.d, # Docetaxel vs Selpercatinib
                          jagsmod=modseq.i[[finalmod]],
                          refmod=refmod,
                          reftrt="Selpercatinib"
                          )

adj.d <- apply(d[,-which(hrnames=="Selpercatinib"), drop=FALSE],
               MARGIN=2, 
               FUN=function(x) {x-adj.d})
adj.d <- cbind(matrix(0, ncol=1, nrow=nrow(adj.d)), adj.d)


g <- plot_st1_survival(modseq.i=adj.jagsmod, 
                  times=seq(1, 52*3, length.out = 100), 
                  refstudy=refstudy, 
                  refmod=refmod,
                  trtnames = hrnames[c(4,1:3)], # Treatment names of constant HR
                  d=adj.d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```



# Survival predictions for ST1, Non-squamous, PDL1 <1%, RET fusion +

Selected reference for ST1 RET fusion + (non-squamous) population is Selpercatinib from **LIBRETTO-001**.

```{r}
# plot.treats <- all.treats[!all.treats %in% c("Sotorasib",
#                                              "Pembrolizumab",
#                                              "Nivolumab")]
plot.treats <- c("Selpercatinib", "Atezolizumab",
                 "Docetaxel", "Docetaxel-Nintedanib", "Pemetrexed + Carboplatin")

modseq.i <- modseq.0
finalmod <- candmod$model[1]
refmod <- refseq.ret[[finalmod]]
refstudy <- "LIBRETTO-001"
pdl1 <- "<1%"
mutation <- "RET fusion +ve"
times <- seq(1, 52*3, length.out = 100)
hist <- "non-squamous"
```

```{r, results="hide", fig.cap=paste("Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial) of PFS for all treatments at ST1 for PDL1", pdl1,",", hist, "patients,", mutation, "mutation.")}
hrnames <- attributes(hrmod)$trtnames

# Select d values for Docteaxel vs Selpercatinib
adj.d <- d[,which(hrnames=="Selpercatinib"), drop=FALSE]

# Adjust FP model to make it relative to Selpercatinib by applying constant HR
adj.jagsmod <- fp_applyhr(d=adj.d, # Docetaxel vs Selpercatinib
                          jagsmod=modseq.i[[finalmod]],
                          refmod=refmod,
                          reftrt="Selpercatinib"
                          )

adj.d <- apply(d[,-which(hrnames=="Selpercatinib"), drop=FALSE],
               MARGIN=2, 
               FUN=function(x) {x-adj.d})
adj.d <- cbind(matrix(0, ncol=1, nrow=nrow(adj.d)), adj.d)


g <- plot_st1_survival(modseq.i=adj.jagsmod, 
                  times=seq(1, 52*3, length.out = 100), 
                  refstudy=refstudy, 
                  refmod=refmod,
                  trtnames = hrnames[c(4,1:3)], # Treatment names of constant HR
                  d=adj.d,
                  plot.treats=plot.treats) + 
  xlab("Time (months)")

plot(g)
```

```{r, eval=FALSE}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq.i[[finalmod]], 
                     refstudy=refstudy,
                     refmod = refmod,
                     treatments = plot.treats,
                     quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```

