---
title: "NSCLC_Outputs - NS2"
author: "Hugo Pedder, Ayman Sadek"
date: "2023-11-03"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  options(knitr.kable.NA = '\\-'),
  fig.height=5, 
  fig.width=7
  )
```
```{r, eval=FALSE, include=FALSE}
devtools::install_github("hugaped/BristolTAG")
```
```{r, include=FALSE}
library(BristolTAG)
library(survival)
library(ggplot2)
library(tidyverse)
```

This document can be used as a template to generate outputs for each node for the NSCLC report. It outputs the following into a Word document (so can easily be copied into the main report):

* Log-log plots for each included study
* Table of model fit statistics
* Plots of KM and fitted survival curves for reference study for best fitting model(s)
* Plots of time-varying (implied) HRs for best fitting model(s)
* If evidence loops exist then also provides model fit results for the Unrelated Mean Effects model and dev-dev plots for the selected model
* Predicted survival curves for selected model for use in economic model (including extrapolation)

## Load model results

```{r}
modseq1 <- readRDS(file="JAGS_Results/NS2_S2_PFS_fpoly1_Analysis1.RDS")
modseq2 <- readRDS(file="JAGS_Results/NS2_S2_PFS_fpoly2_Analysis1.RDS")
modseq <- append(modseq1, modseq2)
class(modseq) <- "sequence.fpoly"
```


## Load dataset

```{r}
ipd <- attributes(modseq[[1]])$ipd

anova <- anova_data(timepoints=seq(0,72, by=1),
                    df=ipd)
```

## Log-log plots

```{r, fig.cap="Log-log plots for PFS for studies included in node NS2. Separation of the two lines indicates violation of the proportional hazards assumption"}
ipd <- attr(modseq1[[1]], "ipd")

loglog_plot(ipd)
```


## Model fit statistics

```{r}
modfit <- summary(modseq)

noconv <- subset(modfit, converged==FALSE)
modfit <- subset(modfit, converged==TRUE)

modfit <- rbind(summary(modseq1), summary(modseq2))

# Drop models with errors
modfit <- modfit[!is.na(modfit$converged),]

modfit <- arrange(modfit, DIC)

candmod <- modfit[c(1:3),]
```

```{r}
# Only report FP powers
knitr::kable(modfit[,c(-1,-7)], col.names=c("Power 1", "Power 2", "Residual deviance", "pV", "DIC"),
                  digits=1, 
                  caption=paste0("Model fit statistics for successfully converged fractional polynomial models run on PFS for node NS2 . Power 1 and Power 2 represent fractional polynomial powers. 1st order fractional polynomials only have a single power parameter (Power 1). Total number of data points = ", nrow(anova$aggregate)))
```

Based on this, candidate models are the following:

```{r}
knitr::kable(candmod[,c(-1,-7)], col.names=c("Power 1", "Power 2", "Residual deviance", "pV", "DIC"),
                  digits=1, 
                  caption=paste0("Model fit statistics for candidate fractional polynomial models run on PFS for node NS2 and S2. Power 1 and Power 2 represent fractional polynomial powers. 1st order fractional polynomials only have a single power parameter (Power 1). Total number of data points = ", nrow(anova$aggregate)))
```


## Plots of time-varying HRs

These are shown only for the 4 candidate models, but additional ones could be specified here.

```{r}
hazardrats <- data.frame()
for (mod in seq_along(candmod$model)) {
  hr <- hrcalc(modseq[[candmod$model[mod]]], times=seq(1, 150, length.out = 100), eform=TRUE)
  hr <- hr$summary %>% mutate(model=candmod$model[mod])
  hazardrats <- rbind(hazardrats, hr)
}
```


Plot panels of time-varying HRs for candidate models:

```{r}
reftrt <- "Chemotherapy"

out.df <- hazardrats

trtnames <- attr(modseq[[1]], "trtnames")

out.df$trt1 <- factor(out.df$trt1, labels=trtnames, levels=trtnames)

cols <- RColorBrewer::brewer.pal(dplyr::n_distinct(out.df$trt1), "Set1")

out.df <- subset(out.df, trt2==reftrt)
cols <- cols[unique(as.numeric(out.df$trt1))]

out.df$model <- factor(out.df$model)

g <- ggplot2::ggplot(out.df, ggplot2::aes(x=time, 
                                          #ymin=`97.5%`, ymax=`2.5%`, # Commenting out makes y-axis scales better
                                          y=`50%`,
                        color=trt1, fill=trt1, linetype=trt1)) +
  ggplot2::geom_line() +
  #ggplot2::geom_ribbon(alpha=0.3) +
  ggplot2::facet_wrap(~model) +
  ggplot2::xlab("Time") +
  ggplot2::ylab("HR") +
  ggplot2::theme_bw() +
  ggplot2::ggtitle(paste0("Time-varying relative effects vs treatment ", unique(out.df$trt2))) +
  ggplot2::scale_fill_manual(name = "Treatment", values=cols) +
  ggplot2::scale_color_manual(name = "Treatment", values=cols) +
  ggplot2::scale_linetype_discrete(name = "Treatment")

plot(g)
```

Based on the above plots, the FP_-0.5_0 suggests HRs increase over time continuously for PPCT and Atezolizumab are implausible. The others are perhaps "possible" but I think the most plausible would be the one that shows the most similarity in the longer term (FP_-0.5_-0.5). It's also the one with the lowest DIC.

Time-varying HRs for a single model with lowest DIC (if needed):

```{r, fig.cap="Time-varying (implied) hazard ratios for all treatments versus Chemotherapy, estimated from 2nd order fractional polynomial of PFS for NS2 & S2. Shaded regions represent 95%CrIs"}
hazardrats <- hrcalc(modseq[[candmod$model[1]]], times=seq(1, 150, length.out = 100), eform=TRUE)
g <- plot(hazardrats, reftrt="Chemotherapy")
g + geom_line(linewidth=0.8) +
  coord_cartesian(ylim=c(0,7.5))
```


# Survival predictions

## Plot of survival predictions and KM data for each study

Plot with KM for plausible model with lowest DIC, 2nd order fractional polynomial:


```{r, results="hide", fig.cap="Predicted survival curves for IMpower110, KEYNOTE024, KEYNOTE189, and KEYNOTE042 estimated from selected 2nd order fractional polynomial of PFS for NS2 & S2 including KEYNOTE-042. Survival predictions are plotted as coloured lines with shaded 95%CrIs. Kaplan-Meier data from the study are plotted as black solid lines."}
g <- studykm_survplot(modseq[[candmod$model[1]]]) +
  geom_km(anova$ipd) +
  ylab("PFS")
plot(g)
```


```{r, results="hide", fig.cap="Predicted survival curves for studies estimated from selected 2nd order fractional polynomial of PFS for NS2 including KEYNOTE-042. Survival predictions are plotted as coloured lines with shaded 95%CrIs. Kaplan-Meier data from the study are plotted as black solid lines."}
studies <- c("IMpower110", "KEYNOTE024", "KEYNOTE042", "KEYNOTE189")
g <- studykm_survplot(modseq[[candmod$model[1]]],
                      studies=studies
                      ) +
  geom_km(subset(anova$ipd, study %in% studies)) +
  ylab("PFS")
plot(g)
```


```{r, results="hide", fig.cap="Predicted survival curves for studies estimated from selected 2nd order fractional polynomial of PFS for S2 including KEYNOTE-042. Survival predictions are plotted as coloured lines with shaded 95%CrIs. Kaplan-Meier data from the study are plotted as black solid lines."}
studies <- c("IMpower110", "KEYNOTE024", "KEYNOTE042", "KEYNOTE407")
g <- studykm_survplot(modseq[[candmod$model[1]]],
                      studies=studies
                      ) +
  geom_km(subset(anova$ipd, study %in% studies)) +
  ylab("PFS")
plot(g)
```


This model appears to be a less good fit for KEYNOTE407 than the other studies, but this is likely due to the difference in results from KEYNOTE189 and KEYNOTE407 since they analyse the same comparison (but with different histologies). 

It's also a poor fit for KEYNOTE024, probably due to the inclusion of KEYNOTE042.


## Survival predictions for NS2

Selected reference study for NS2 is **KEYNOTE189**

### Plots of survival predictions for different models (NS2 including KEYNOTE-042)

```{r}
surv <- data.frame()
for (mod in seq_along(candmod$model)) {
  smod <- survcalc(modseq[[candmod$model[mod]]], refstudy="KEYNOTE189", 
                times=seq(1, 150, length.out = 100))
  smod <- smod$S %>% mutate(model=candmod$model[mod])
  surv <- rbind(surv, smod)
}
```

```{r}
out.df <- surv

trtnames <- attr(modseq[[1]], "trtnames")
out.df$treatment <- factor(out.df$treatment, labels=trtnames, levels=trtnames)

# Define colours
cols <- RColorBrewer::brewer.pal(dplyr::n_distinct(trtnames), "Set1")

# Subset by treatments
# out.df <- subset(out.df, treatment %in% treats)
cols <- cols[unique(as.numeric(out.df$treatment))]

out.df$model <- factor(out.df$model)

# capt <- paste0("Fractional polynomial; P1 = ", surv$P1, ifelse(!is.null(surv$P2), paste0(", P2 = ", surv$P2), ""))
# capt <- paste(capt, paste("Reference study:", attr(surv, "refstudy")), sep="\n")
capt <-paste("Reference study:", attr(modseq[[1]], "refstudy"))

g <- ggplot2::ggplot(out.df, ggplot2::aes(x=time, ymin=`97.5%`, ymax=`2.5%`, y=`50%`,
                        color=treatment, fill=treatment, linetype=treatment)) +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(~model) +
  ggplot2::xlab("Time") + ggplot2::ylab("PFS") +
  ggplot2::theme_bw() +
  ggplot2::scale_fill_manual(name = "Treatment", values=cols) +
  ggplot2::scale_color_manual(name = "Treatment", values=cols) +
  ggplot2::scale_linetype_discrete(name = "Treatment") +
  ggplot2::labs(caption=capt)

plot(g)
```


### Plot of survival predictions and KM data for reference study (NS2)

Plot with KM for most plausible model with lowest DIC, 2nd order fractional polynomial:

```{r, results="hide", fig.cap="Predicted survival curves for KEYNOTE189, estimated from 2nd order fractional polynomial (-0.5,-0.5) of PFS for NS2 including KEYNOTE-042. Survival predictions are plotted as coloured lines with shaded 95%CrIs. Kaplan-Meier data from the study are plotted as black solid lines."}
surv <- survcalc(modseq[[candmod$model[1]]], times=seq(1, max(ipd$time[ipd$study=="KEYNOTE189"]), length.out = 100),
                 refstudy="KEYNOTE189")
g <- plot(surv, quantity = "S", treats = c("PPCT", "Chemotherapy"), overlay.km = TRUE) +
  ylab("PFS")
plot(g)
```

### Model fit results for UME (NS2)

No closed loops for this network

### Dev-dev plots for UME vs NMA (NS2)

No closed loops for this network


### Predicted survival curves for selected model with extrapolation (NS2)

I'll just choose one here.

```{r, results="hide", fig.cap="Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial -0.5,-0.5) of PFS for all treatments at NS2 including KEYNOTE-042."}
surv <- survcalc(modseq[[candmod$model[1]]], times=seq(1, 52*3, length.out = 100),
                 refstudy="KEYNOTE189")
g <- plot(surv, quantity = "S", plotinterval = FALSE) + geom_line(linewidth=1) +
  ylab("PFS")
plot(g)
```

Median survival for each treatment within selected model:

```{r}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq[[candmod$model[1]]], refstudy="KEYNOTE189",
                 quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```

### Multivariate normal parameters from candidate  (NS2)

These will be saved to an excel file.

```{r}
library(officer)

info.df <- data.frame("Title"=c("Fractional polynomial multivariate normal distribution of MCMC samples - means and covariances for key model parameters",
                                      # "Parameters named by the study name refer to the reference study ('baseline') effect for each fractional polynomial coefficient (1-3)",
                                      paste0("Parameters named by the treatment refer to the relative treatment effect for each fractional polynomial coefficient (1-3) versus the network reference (", attributes(modseq[[1]])$trtnames[1], ")")))

# Choose save location
wb <- openxlsx::createWorkbook(title="NS2_Analysis1")
openxlsx::addWorksheet(wb=wb, sheetName="Info")
openxlsx::writeDataTable(wb=wb, sheet="Info", 
                         x=info.df)

for (i in 1:nrow(candmod)) {
  
  mod <- modseq[[candmod$model[i]]]
  
  sheetnam <- paste("FP", mod$model$data()$P1, mod$model$data()$P2, sep="_")
  openxlsx::addWorksheet(wb=wb, sheetName=sheetnam)
  
  # mvn <- output_coda_fp(mod, format="mvn",
  #                       refstudy="KEYNOTE189")
  mvn <- output_coda_fp(mod, format="mvn",
                        refstudy=NULL)
  
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$mean), rowNames = TRUE)
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$covar), startCol=4,
                           rowNames = TRUE, colNames = TRUE)
}

openxlsx::saveWorkbook(wb=wb, file="MVN_NS2_Analysis1.xlsx", overwrite=TRUE)
```



## Survival predictions for S2

Selected reference study for S2 is **KEYNOTE407**

### Plots of survival predictions for different models (S2)

```{r}
surv <- data.frame()
for (mod in seq_along(candmod$model)) {
  smod <- survcalc(modseq[[candmod$model[mod]]], refstudy="KEYNOTE407", 
                times=seq(1, 150, length.out = 100))
  smod <- smod$S %>% mutate(model=candmod$model[mod])
  surv <- rbind(surv, smod)
}
```

```{r}
out.df <- surv

trtnames <- attr(modseq[[1]], "trtnames")
out.df$treatment <- factor(out.df$treatment, labels=trtnames, levels=trtnames)

# Define colours
cols <- RColorBrewer::brewer.pal(dplyr::n_distinct(trtnames), "Set1")

# Subset by treatments
# out.df <- subset(out.df, treatment %in% treats)
cols <- cols[unique(as.numeric(out.df$treatment))]

out.df$model <- factor(out.df$model)

# capt <- paste0("Fractional polynomial; P1 = ", surv$P1, ifelse(!is.null(surv$P2), paste0(", P2 = ", surv$P2), ""))
# capt <- paste(capt, paste("Reference study:", attr(surv, "refstudy")), sep="\n")
capt <-paste("Reference study:", attr(modseq[[1]], "refstudy"))

g <- ggplot2::ggplot(out.df, ggplot2::aes(x=time, ymin=`97.5%`, ymax=`2.5%`, y=`50%`,
                        color=treatment, fill=treatment, linetype=treatment)) +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(~model) +
  ggplot2::xlab("Time") + ggplot2::ylab("PFS") +
  ggplot2::theme_bw() +
  ggplot2::scale_fill_manual(name = "Treatment", values=cols) +
  ggplot2::scale_color_manual(name = "Treatment", values=cols) +
  ggplot2::scale_linetype_discrete(name = "Treatment") +
  ggplot2::labs(caption=capt)

plot(g)
```


### Plot of survival predictions and KM data for reference study (S2)

Plot with KM for most plausible model with lowest DIC, 2nd order fractional polynomial:

```{r, results="hide", fig.cap="Predicted survival curves for KEYNOTE407, estimated from 2nd order fractional polynomial (-0.5,-0.5) of PFS for S2 including KEYNOTE-042. Survival predictions are plotted as coloured lines with shaded 95%CrIs. Kaplan-Meier data from the study are plotted as black solid lines."}
surv <- survcalc(modseq[[candmod$model[1]]], times=seq(1, max(ipd$time[ipd$study=="KEYNOTE407"]), length.out = 100),
                 refstudy="KEYNOTE407")
g <- plot(surv, quantity = "S", treats = c("PPCT", "Chemotherapy"), overlay.km = TRUE) +
  ylab("PFS")
plot(g)
```

### Model fit results for UME (S2)

No closed loops for this network

### Dev-dev plots for UME vs NMA (S2)

No closed loops for this network


### Predicted survival curves for selected model with extrapolation (S2)

I'll just choose one here.

```{r, results="hide", fig.cap="Predicted survival curves and extrapolations for the selected model (2nd order fractional polynomial -0.5,-0.5) of PFS for all treatments at S2 including KEYNOTE-042."}
surv <- survcalc(modseq[[candmod$model[1]]], times=seq(1, 52*3, length.out = 100),
                 refstudy="KEYNOTE407")
g <- plot(surv, quantity = "S", plotinterval = FALSE) + geom_line(linewidth=1) +
  ylab("PFS")
plot(g)
```

Median survival for each treatment within selected model:

```{r}
# Note that interval has to be wide enough to allow for ALL potential MCMC median survival estimates
surv <- survquantile(modseq[[candmod$model[1]]], refstudy="KEYNOTE407",
                 quantile=0.5, interval=c(0.1,100))
tab <- print(surv)

knitr::kable(tab, digits=2, 
                  caption="Median survival for the fractional polynomial model reported above")
```


### Multivariate normal parameters from candidate  (S2)

These will be saved to an excel file.

```{r}
library(officer)

info.df <- data.frame("Title"=c("Fractional polynomial multivariate normal distribution of MCMC samples - means and covariances for key model parameters",
                                      # "Parameters named by the study name refer to the reference study ('baseline') effect for each fractional polynomial coefficient (1-3)",
                                      paste0("Parameters named by the treatment refer to the relative treatment effect for each fractional polynomial coefficient (1-3) versus the network reference (", attributes(modseq[[1]])$trtnames[1], ")")))

# Choose save location
wb <- openxlsx::createWorkbook(title="S2_Analysis1")
openxlsx::addWorksheet(wb=wb, sheetName="Info")
openxlsx::writeDataTable(wb=wb, sheet="Info", 
                         x=info.df)

for (i in 1:nrow(candmod)) {
  
  mod <- modseq[[candmod$model[i]]]
  
  sheetnam <- paste("FP", mod$model$data()$P1, mod$model$data()$P2, sep="_")
  openxlsx::addWorksheet(wb=wb, sheetName=sheetnam)
  
  # mvn <- output_coda_fp(mod, format="mvn",
  #                       refstudy="KEYNOTE407")
  mvn <- output_coda_fp(mod, format="mvn",
                        refstudy=NULL)
  
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$mean), rowNames = TRUE)
  openxlsx::writeDataTable(wb=wb, sheet=sheetnam, data.frame(mvn$covar), startCol=4,
                           rowNames = TRUE, colNames = TRUE)
}

openxlsx::saveWorkbook(wb=wb, file="MVN_S2_Analysis1.xlsx", overwrite=TRUE)
```
